Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-04-11 doc/manuscript/manuscript.tex
some small changes to the yield summary table function. Added a table to the utility tables list to convert summary table column names to more easily readible column names

The data for seed yield, seed oil, and seed protein contents were
analyzed using a mixed model with the metan\citep{r_metan} R package.
Environment, replication nested with environment, and the interaction of
genotype with environment were considered to be random effects while
genotype was considered to be a fixed effect.

@@

>>>>

The data for seed yield, seed oil, and seed protein contents were
analyzed using a mixed model with the
metan\citep{olivotoMetanPackageMultienvironment2020} R package.
Environment, replication nested with environment, and the interaction of
genotype with environment were considered to be random effects while
genotype was considered to be a fixed effect.

@@

\centering
\begin{tabular}{l|r|r|l|l|l|r|r|l|l|l|r|r|l|l|l|r|r|l|l|l}
\hline
\multicolumn{1}{c|}{} & \multicolumn{5}{c|}{Protein + Oil} & \multicolumn{5}{c|}{Protein} & \multicolumn{5}{c|}{Yield} & \multicolumn{5}{c}{Oil} \\
\cline{2-6} \cline{7-11} \cline{12-16} \cline{17-21}
genotype & value & rank & test\_avg & check\_avg\_value & msd & value & rank & test\_avg & check\_avg\_value & msd & value & rank & test\_avg & check\_avg\_value & msd & value & rank & test\_avg & check\_avg\_value & msd\\
\hline
LMN09-119 & 69.44 & 1 &  &  &  & 51.67 & 1 &  &  &  & 40.82 & 17 &  &  &  & 17.77 & 20 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1855 & 68.07 & 2 &  &  &  & 47.51 & 4 &  &  &  & 43.17 & 10 &  &  &  & 20.57 & 14 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1632-1 & 67.49 & 3 &  &  &  & 46.81 & 5 &  &  &  & 45.73 & 6 &  &  &  & 20.67 & 11 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1763 & 67.46 & 4 &  &  &  & 47.98 & 2 &  &  &  & 39.45 & 18 &  &  &  & 19.48 & 18 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1632-2 & 67.41 & 5 &  &  &  & 46.79 & 6 &  &  &  & 46.34 & 5 &  &  &  & 20.62 & 12 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1595 & 67.04 & 6 &  &  &  & 47.73 & 3 &  &  &  & 43.52 & 9 &  &  &  & 19.30 & 19 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1731 & 66.66 & 7 &  &  &  & 46.27 & 8 &  &  &  & 43.16 & 11 &  &  &  & 20.40 & 15 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1674 & 66.38 & 8 &  &  &  & 45.48 & 9 &  &  &  & 44.26 & 7 &  &  &  & 20.90 & 8 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1572 & 66.26 & 9 &  &  &  & 45.38 & 10 &  &  &  & 38.58 & 19 &  &  &  & 20.88 & 9 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N09-09 & 66.26 & 10 &  &  &  & 46.74 & 7 &  &  &  & 41.63 & 14 &  &  &  & 19.52 & 17 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1956 & 66.13 & 11 &  &  &  & 45.26 & 12 &  &  &  & 34.79 & 20 &  &  &  & 20.87 & 10 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1682 & 65.87 & 12 &  &  &  & 45.27 & 11 &  &  &  & 43.64 & 8 &  &  &  & 20.60 & 13 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1751 & 65.23 & 13 &  &  &  & 44.85 & 13 &  &  &  & 41.59 & 15 &  &  &  & 20.37 & 16 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1635 & 65.22 & 14 &  &  &  & 43.79 & 16 &  &  &  & 46.45 & 4 &  &  &  & 21.42 & 3 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1604 & 65.19 & 15 &  &  &  & 43.99 & 14 &  &  &  & 43.15 & 12 &  &  &  & 21.20 & 5 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1620 & 65.15 & 16 &  &  &  & 43.98 & 15 &  &  &  & 46.54 & 3 &  &  &  & 21.17 & 6 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
N18-1641 & 64.83 & 17 &  &  &  & 43.73 & 17 &  &  &  & 41.99 & 13 &  &  &  & 21.10 & 7 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
Dilday & 63.54 & 18 &  &  &  & 41.40 & 19 &  &  &  & 46.78 & 2 &  &  &  & 22.15 & 2 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
NC-Raleigh & 63.53 & 19 &  &  &  & 40.32 & 20 &  &  &  & 41.04 & 16 &  &  &  & 23.21 & 1 &  &  & \\
\cline{1-3}
\cline{7-8}
\cline{12-13}
\cline{17-18}
Dunphy & 63.34 & 20 & \multirow{-20}{*}{\raggedright\arraybackslash 66.02} & \multirow{-20}{*}{\raggedright\arraybackslash 65.22} & \multirow{-20}{*}{\raggedright\arraybackslash 0.73} & 41.94 & 18 & \multirow{-20}{*}{\raggedright\arraybackslash 45.34} & \multirow{-20}{*}{\raggedright\arraybackslash 44.41} & \multirow{-20}{*}{\raggedright\arraybackslash 1.09} & 47.33 & 1 & \multirow{-20}{*}{\raggedright\arraybackslash 43} & \multirow{-20}{*}{\raggedright\arraybackslash 43.52} & \multirow{-20}{*}{\raggedright\arraybackslash 7.08} & 21.41 & 4 & \multirow{-20}{*}{\raggedright\arraybackslash 20.68} & \multirow{-20}{*}{\raggedright\arraybackslash 20.81} & \multirow{-20}{*}{\raggedright\arraybackslash 0.77}\\
\hline
\end{tabular}
\end{table}
